Implementation of Concurrent Hash Tables in Java

### 2022-04-29 paper.tex
Changes
Update paper.tex

\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Implementation of Concurrent Hash Tables in Java}

@@

    // Increase capacity
    capacity++;
    return true;
}
\end{lstlisting}
\section{Experimental Results}
We began by testing how the standard hash table will performed when run sequentially, and then when multithreaded. 
After those tests, we created a locking hash table and proceeded to run tests on that version. 
After both of those tests, we deicded it would be a good idea to test our hash tables to Java's native concurrent hash map, the closest thing to a concurrent hash table Java has to offer natively.
Our measurement for testing was timing how long each hash table takes to add a specific amount of numbers, make sure each one was added, remove all those numbers, and then make sure each was removed. 
We recorded all the measurements into a CSV file and used a Python program to analyze the numbers, using Pandas to do the math and Matplotlib and Seaborn to visualize the data gathered. 
We were able to gather a plentiful amount of information regarding each hash table and the time it takes to do these processes. 
The data we gathered includes total time taken, the CPU used, the amount of tests, the time it took to do each test for each hash table, the average, low, and high times, and the standard deviation. All times recorded are in millisecconds. 
\begin{figure}[htbp]
    \centerline{\includegraphics[width=90mm,scale=1]{250trials.png}}
    \caption{Graphs of each test for each hash table. The x-axis is the test number, the y-axis is the time in ms the test took. }
    \label{fig}
\end{figure}

\begin{table}[htbp]
    \caption{Experimental Results}
    \begin{center}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    \textbf{Data}&\multicolumn{4}{|c|}{\textbf{Hash Table Version}} \\
    \cline{2-5} 
    \textbf{Calculation} & \textbf{\textit{Nonlocking}}& \textbf{\textit{Threaded}}& \textbf{\textit{Locked Threaded}}& \textbf{\textit{Java}} \\
    \hline
    \textbf{Average}& 8,135 ms& 130 ms&  5 ms& 272 ms\\
    \hline
    \textbf{High}& 10,978 ms& 145 ms&  66 ms& 1,499 ms\\
    \hline
    \textbf{Low}& 8164 ms& 118 ms&  4 ms& 247 ms\\
    \hline
    \textbf{Deviation}& 376.3 ms& 4.5 ms&  4.1 ms& 78.7 ms\\
    \hline
    \textbf{Total time}&\multicolumn{4}{|c|}{\textbf{2,180,629 ms}} \\
    \hline
    \multicolumn{5}{l}{Nonlocking and Threaded are the same class, but the latter was concurrently tested}
    \end{tabular}
    \label{tab1}
    \end{center}
\end{table}

>>>>

\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tabularx}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Implementation of Concurrent Hash Tables in Java}

@@

    // Increase capacity
    capacity++;
    return true;
}
\end{lstlisting}

The code outlined in "Listing 1" is the put() method for the coarse-grain hash table created for this project. As it is a course grain hash table,
it utilizes the \emph{synchronized} keyword to make a lock on this function, meaning that if one thread were to be in the middle of a call to this function
then any thread that attempted to call it would have to wait until the original thread finished it's function call. Since this implementation uses a fixed size 
hash table, the method will first check to see if the hash table has reached it's maximum capacity. If the hash table is full, then the method returns false,
indicating that the attempt to put the item into the hash table was unsuccessful. In the case that the hash table still has unused memory, then the method
will create a key for the item by hashing it, and checks to see if the memory location associated with that key has been used yet.
\section{Experimental Results}
We began by testing how the standard hash table will performed when run sequentially, and then when multithreaded. 
After those tests, we created a locking hash table and proceeded to run tests on that version. 
After both of those tests, we deicded it would be a good idea to test our hash tables to Java's native concurrent hash map, the closest thing to a concurrent hash table Java has to offer natively.
Our measurement for testing was timing how long each hash table takes to add a specific amount of numbers, make sure each one was added, remove all those numbers, and then make sure each was removed. 
We recorded all the measurements into a CSV file and used a Python program to analyze the numbers, using Pandas to do the math and Matplotlib and Seaborn to visualize the data gathered. 
We were able to gather a plentiful amount of information regarding each hash table and the time it takes to do these processes. 
The data we gathered includes total time taken, the CPU used, the amount of tests, the time it took to do each test for each hash table, the average, low, and high times, and the standard deviation. All times recorded are in millisecconds. 
\begin{figure}[htbp]
    \centerline{\includegraphics[width=90mm,scale=1]{250trials.png}}
    \caption{Graphs of each test for each hash table. The x-axis is the test number, the y-axis is the time in ms the test took. }
    \label{fig}
\end{figure}

\begin{table}[htbp]
    \caption{Experimental Results}
    \begin{center}
    \begin{tabularx}{\columnwidth}{|X|X|X|X|X|}
    \hline
    \textbf{Data}&\multicolumn{4}{|c|}{\textbf{Hash Table Version}} \\
    \cline{2-5} 
    \textbf{Calculation} & \textbf{\textit{Nonlocking}}& \textbf{\textit{Threaded}}& \textbf{\textit{Locked Threaded}}& \textbf{\textit{Java}} \\
    \hline
    \textbf{Average}& 8,135 ms& 130 ms&  5 ms& 272 ms\\
    \hline
    \textbf{High}& 10,978 ms& 145 ms&  66 ms& 1,499 ms\\
    \hline
    \textbf{Low}& 8164 ms& 118 ms&  4 ms& 247 ms\\
    \hline
    \textbf{Deviation}& 376.3 ms& 4.5 ms&  4.1 ms& 78.7 ms\\
    \hline
    \textbf{Total time}&\multicolumn{4}{|c|}{\textbf{2,180,629 ms}} \\
    \hline
    \multicolumn{5}{l}{Threaded is Nonlocking but concurrently tested instead}
    \end{tabularx}
    \label{tab1}
    \end{center}
\end{table}
